---
title: "R Notebook"
output: html_notebook
---
```{r}
library(igraph)
```


```{r}
df86<-read.csv("output_data1986(regions).csv",header = T)
df96<-read.csv("output_data1996(regions).csv",header=T)
df06<-read.csv("output_data2006(regions).csv",header=T)
df16<-read.csv("output_data2016(regions).csv",header=T)
```

```{r}
g.86<-df86[which(df86$weight>10000000),]
g86<-graph_from_data_frame(g.86)
g.96<-df96[which(df96$weight>10000000),]
g96<-graph_from_data_frame(g.96)
g.06<-df06[which(df06$weight>10000000),]
g06<-graph_from_data_frame(g.06)
g.16<-df16[which(df16$weight>10000000),]
g16<-graph_from_data_frame(g.16)

```

```{r}
between86<-betweenness(g86)
#between86
col86<-data.frame(unname(between86))
count86<-apply(col86,2,function(c)sum(c==0))
count86
between96<-betweenness(g96)
#between96
col96<-data.frame(unname(between96))
count96<-apply(col96,2,function(c)sum(c==0))
count96
between06<-betweenness(g06)
#between06
col06<-data.frame(unname(between06))
count06<-apply(col06,2,function(c)sum(c==0))
count06
between16<-betweenness(g16)
#between16
col16<-data.frame(unname(between16))
count16<-apply(col16,2,function(c)sum(c==0))
count16
x1<-mean(unname(between86))
x2<-mean(unname(between96))
x3<-mean(unname(between06))
x4<-mean(unname(between16))
averageBetween<-data.frame(average=c(x1,x2,x3,x4),year=c("1986","1996","2006","2016"))
```
```{r}
library(ggplot2)
ggplot(data=averageBetween,aes(x=year,y=average)) +
  geom_bar(stat="identity") + ggtitle("Average betweenness over four decades")
```

This suggests that as the years have progressed more countries have devloped higher betweeness resulting in more defined trade patterns.(i.e a handful of countries very low betweeness means they are removed from trading but since the average as increased over the years it is suggesting that countries are becoming more invovled in trading(enforces globalization) )
```{r}
close86<-closeness(g86)
#between86
close96<-closeness(g96)
#between96
close06<-closeness(g06)
#between06
close16<-closeness(g16)
#between16
y1<-mean(unname(close86))
y2<-mean(unname(close96))
y3<-mean(unname(close06))
y4<-mean(unname(close16))
averageclose<-data.frame(average=c(y1,y2,y3,y4),year=c("1986","1996","2006","2016"))
```


```{r}
ggplot(data=averageclose,aes(x=year,y=average)) +
  geom_bar(stat="identity") + ggtitle("Average closeness over four decades")
```
This shows that over the decades countries have become more connected resulting in more direct trade patterns

```{r}
rank86<-page.rank(g86)
#between86
rank96<-page.rank(g96)
#between96
rank06<-page.rank(g06)
#between06
rank16<-page.rank(g16)
#between16

z1<-mean(unname(rank86$vector))
z2<-mean(unname(rank96$vector))
z3<-mean(unname(rank06$vector))
z4<-mean(unname(rank16$vector))
averageRank<-data.frame(average=c(z1,z2,z3,z4),year=c("1986","1996","2006","2016"))
```
```{r}
ggplot(data=averageRank,aes(x=year,y=average)) +
  geom_bar(stat="identity") + ggtitle("Average page rank over four decades")
```
```{r}
wc86<-walktrap.community(g86,steps = 20)
wc96<-walktrap.community(g96,steps=20)
wc06<-walktrap.community(g06,steps=20)
wc16<-walktrap.community(g16,steps = 20)
sizes(wc86)
sizes(wc96)
sizes(wc06)
sizes(wc16)

```

```{r}
g86$community<-membership(wc86)

n<-max(g86$community)
group<-data.frame(c(g86$community))

for (i in 1:n){

print(subset(group,c(g86$community)==i))
}

```
```{r}
g96$community<-membership(wc96)

n<-max(g96$community)
group1<-data.frame(c(g96$community))

for (i in 1:n){

print(subset(group1,c(g96$community)==i))
}
```
```{r}
g06$community<-membership(wc06)

n<-max(g06$community)
group2<-data.frame(c(g06$community))

for (i in 1:n){

print(subset(group2,c(g06$community)==i))
}
```
```{r}
g16$community<-membership(wc16)

n<-max(g16$community)
group3<-data.frame(c(g16$community))

for (i in 1:n){

print(subset(group3,c(g16$community)==i))
}
```